%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Scholarly and Professional Activities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student} % Affiliation/role
    {EPAM Systems (Java Laboratory)} % Organization/group
    {Lviv, Ukraine} % Location
    {Nov. 2020 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained theoretical knowledge about OOP, GRASP/SOLID principles and practical skills with Java Core, JUnit, Mockito, JDBC, H2.}
        \item {Developed personal web-project that helps in managing tests \& questionnaires. Developed on Servlets and JSP pages, without frameworks, published on my github account.}
        \item {Refactored personal web-project from Java Servlets into Spring application with REST API endpoints.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Consultant} % Affiliation/role
    {CAD Department of Lviv Polytechnic} % Organization/group
    {Lviv, Ukraine} % Location
    {Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted in creating new curriculum subject "Methods of Business Communications".}
        \item {Shared my Sales Management commercial experience and recommended literature with professors.}
        \item {Prepared curriculum practicum tasks as laboratory works.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Member Of Organizing Committee} % Affiliation/role
    {15th CADSM Conference by CAD Department of Lviv Polytechnic } % Organization/group
    {Lviv, Ukraine} % Location
    {Sep. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created an Instagram account @cadsm\_conference.}
        \item {Developed and managed content, grew audience.}
        \item {Gathered e-mail list of potential interested universities for the marketing campaign.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Ternopil Without Problems Hackaton} % Organization/group
    {Ternopil, Ukraine} % Location
    {May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Co-creator of the concept of "AR Reproduction of the Destroyed Historical Architectural Heritage" in order to solve the problem of tourism in Ternopil.}
        \item {Presentation and speech composer, represented team and solution in front of the audience.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
