%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Symphony Solutions} % Organization
    {Lviv, Ukraine} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of an urban mobility solution for public transport. Java Spring  applications as microservices architecture, deployed as K8S pods on AWS.}
        \item {Proposed and implemented solution for role-based security based on Spring Security with documentation for further management.}
        \item {Introduced and developed a new microservice integrated with Flowable BPMN engine.}
        \item {Implemented internal money wallet with transaction logging and REST API.}
        \item {REST API development: from OAS definition to covering implemented logic by unit and e2e tests.}
        \item {Knowledge sharing - assistance for new on-boarded engineers regarding project architecture, GitLab pipelines, development approach and etc.}
        \item {Active participation in dev-talks and architecture discussions.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Etiya Inc.} % Organization
    {Lviv, Ukraine} % Location
    {May. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and maintenance of software applications designed for Telecom Industry in Canada.}
        \item {Deep down investigation, identifying the root causes of problems and resolving.}
        \item {Managing integration processes within different IT systems.}
      \end{cvitems}
    }
%---------------------------------------------------------
\newline
\newline
  \cventry
    {Sales Manager} % Job title
    {Webitel} % Organization
    {Lviv, Ukraine} % Location
    {Feb. 2019 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Providing Customer Center and CRM solutions for CIS, Europe and US regions. Products line: Creatio CRM, Webitel IP-PBX.}
        \item {Achieved good personal reputation in partners network that led to receiving inbound leads from recommendations.}
        \item {Managed and made a sale with company from Fortune 500 list.}
        \item {Development of sales kit and strategies: presentations, key advantages, proof of concept, individual presentations, project road-maps.}
        \item {Representing company and lead generation at conferences: Terrasoft Accelerate Global Conference, Bank Online MFO Summit in Kyiv.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}